### 2021-04-08 Chapter-5/Chapter-5.tex
Updates from Overleaf

Second, many side-channel leakage detection tools rely on some techniques like symbolic executions, taint analysis, and abstract interpretations~\cite{203878,182946,Brotzman19Casym,236338}. Those methods need to consider the semantics of each ISA instruction, which is tedious. So they build the tool on the top of existing binary analysis frameworks. Due to the limitations of binary analysis frameworks, it is hard to apply existing methods to analyze side-channels in non-cryptography libraries. For many other applications like machine learning, media, and graphic libraries built on the top architecture-dependent libraries (e.g., Intel MKL~\cite{wang2014intel}), those tools can not handle it. Moreover, existing binary analysis frameworks (e.g., Angr~\cite{shoshitaishvili2016state}) are limited to analyze floating-point instructions. But the functionality of those applications heavily depends on floating-point calculations.

Third, while many existing works can detect side-channel leakages, few of them can assess how severity level of those vulnerabilities~\cite{203878,182946,Brotzman19Casym,236338,217537,Wichelmann:2018:MFF:3274694.3274741}. There are some tools~\cite{182946,Chattopadhyay:2017:QIL:3127041.3127044} that can quantify the information leakage.  Those tools usually rely on the abstraction to give an upper bound estimation of each leakage site, which is useful to justify the software is secure if the reported leakage is zero. But those tools can not tell software developers how serious each leakage site would be because of the over-approximation they apply when they estimate the amount of leakage. The best way to estimate each leakage's severe level is to exploit the leakage and recover the information. However, the process itself is very tedious and needs a lot of domain knowledge.

To solve the above problem, we propose a method to estimate the effect of each side-channel leakages automatically. We compare the side-channel attack to a communication system and use the channel capacity to quantify the amount of the information flow from the original secret to the observation of an attacker. The method also allows us to combine multiple leakages sites to retrieve the information. The  attack can be seem as a process that reduces the search space of the original sensitive inputs. We use the side-channel vulnerability to divide the input space. If the patterns can unique distinguish the input space, then we think the information is leaked totally. However, in the real cases, many of those side-channel leakage patterns are not enough for us to distinguish each leakage sites, but can still distinguish some of the sensitive inputs. In those cases, we call those leakages partial leaks.

>>>>

Second, many side-channel leakage detection tools rely on some techniques like symbolic executions, taint analysis, and abstract interpretations~\cite{203878,182946,Brotzman19Casym,236338}. It is hard to implement those techniques from scratch. So they build the tool on top of existing binary analysis frameworks. Due to the limitations of existing binary analysis frameworks, it is hard to apply existing methods to analyze side-channels in non-cryptography libraries. For many other applications like machine learning, media, and graphic libraries built on the top architecture-dependent libraries (e.g., Intel MKL~\cite{wang2014intel}), those tools can not handle it. Moreover, some binary analysis frameworks (e.g., Angr~\cite{shoshitaishvili2016state}) are limited in analyzing floating-point instructions. But the functionality of those applications heavily depends on floating-point calculations.

Third, while many existing tools can detect side-channel leakages, few of them can assess how severity level of those vulnerabilities~\cite{203878,182946,Brotzman19Casym,236338,217537,Wichelmann:2018:MFF:3274694.3274741}. There are some tools~\cite{182946,Chattopadhyay:2017:QIL:3127041.3127044} that can quantify the information leakage. Those tools can give an upper bound estimation of each leakage site, which is useful to justify the software is secure if the reported leakage is zero. But those tools can not tell software developers how serious each leakage site would be because of the over-approximation they apply when they estimate the amount of leakage. The best way to estimate each leakage's severe level is to exploit the leakage and recover the information. However, the process itself is very tedious and needs a lot of domain knowledge.

To solve the above problem, we propose a method to estimate the effect of side-channel leakages automatically. We compare the side-channel attack to a communication system and use the channel capacity to quantify the amount of the information flow from the original secret to an attacker's observation. The method also allows us to combine multiple leakages sites to retrieve the information. The attack can be seen as a process that reduces the search space of the original sensitive inputs. We use the side-channel vulnerability to divide the input space. If the patterns can uniquely distinguish the input space, then we think the information is leaked totally. However, in real cases, many of those side-channel leakage patterns are not enough to distinguish each leakage site but can still discern some secret inputs. In those cases, we call those partial leakages leaks.
